Statistical Inference of Transport Mechanisms and Long Time Scale Behavior from Time Series of Solute Trajectories in Nanostructured Membranes

### 2020-08-08 Ben_Manuscripts/hdphmm/response_to_reviewers.tex

\begin{enumerate}[label={Comment \theenumi :}, leftmargin=3.9\parindent]

    %r1_comment1
    \item \textit{The manuscript by Coscia et al. analyzes diffusion and transport of solute molecules
    in a low water content lyotropic liquid crystal using a statistical model developed on the basis 
    of molecular dynamics simulations. The purpose of the statistical model is two-fold; first to 
    extrapolate computed MSDs to longer times to obtain diffusion coefficients, and second to attempt
    to gain increased physical insight on diffusion mechanisms. These issues are important in 
    highly-confined/low-water content nanoporous materials, in which diffusion occurs through complex
    mechanisms and over long timescales. The manuscript will most likely be of interest to the community
    interested in nanoporous materials for separations.}

    Author reply: We thank the reviewer for their thoughtful assessment of our work.

    %r1_comment2
    \item \textit {Unfortunately, because there is no comparison with alternative techniques, it is 
    very difficult to evaluate this new approach relative to previous work that has examined similar 
    issues. There exist numerous other methods for extrapolating MSDs to longer time, which the 
    authors have not discussed. One such method is the “trajectory-extending kinetic Monte Carlo” 
    (TEKMC) approach of Brown and coworkers see e.g. Macromolecules 2010, 43, 9210-9214, 
    Macromolecules 2015, 48, 7346-7358, and J. Phys Chem. B, 2012, 116, 95-103. The authors should 
    %BJC: well Venkat Ganesan just relinquished his anonymity
    %MRS: the paper will get in, I'm sure, and now we know better how he thinks, so all good.
    add a comprehensive discussion of how their approach compares to this and similar methods. The 
    paper would be significantly improved if the authors were to perform and present TEKMC results 
    for their system, so that one could better evaluate the performance of their proposed method.}

@@

    We have also modified the first sentence of the paragraph that follows in order to maintain
    good flow.

    Original text:
    \begin{quote}
    We have already advanced our understanding of LLC monomer design in our previous work
    by building stochastic time series models based on the chemical intuition gained
    from qualitative MD studies of solute transport in an H\textsubscript{II} phase LLC
    membrane.
    \end{quote}

    Modified text:
    \begin{quote}
    Based on the chemical intuition gained from our previous qualitative MD studies of 
    solute transport in an H\textsubscript{II} phase LLC membrane, we have contributed our
    own stochastic modeling approaches with goals similar to both TEKMC and DBP.
    \end{quote}

    %MRS: tweaked below.
    We agree that a full comparison of our method to other methods for computing long timescale 
    diffusion such as TEKMC would be very interesting and instructive but feel it would be better 
    suited as a separate study where we could include a number of approaches, including perhaps
    recent approaches we have developed within our research group.~\cite{coscia_capturing_2020}
    Such a large-scale comparison would take more space and time than would be appropriate for the current paper.
    % We would also prefer to have
    %sufficient time to appropriately implement the technique for our system.
    Although method such as TEKMC seems a
    fairly straightforward approach to implement, it is not immediately clear how we could
    optimally adapt the methodology to a monoclinic unit cell with two dimensional order. 
%    the grids that divide the homogeneous cubic unit cells of the referenced TEKMC studies to 
%    our system which uses a monoclinic unit cell and has 2 dimensional order.

    As stated by the reviewer, there are two goals of our work: to obtain long timescale MSDs and
    to understand mechanisms leading to diffusive behavior. TEKMC may be a suitable alternative 
    approach to obtaining our first goal, but it is not clear that it could give the same level
    of mechanistic insight that the HDP-AR-HMM offers. Although the work by Hanson et al.
    (J. Phys Chem. B, 2012, 116, 95-103) is able to provide physical insight into the effect of
    nanoparticles on diffusion of gaseous penetrants in a polystyrene polymer matrix, it does so
    by testing hypotheses motivated by observations of the diffusion constant (predicted by TEKMC)
    in response to different temperatures and nanoparticle concentrations. This is actually pretty
    in line with the type of analysis we performed in our initial LLC work
    %MRS: you mean your 2nd paper? refer specifically
    where we used the mean squared displacement and the qualitative characteristic of the solute time series in
    order to hypothesize transport mechanisms. In this work we "re-discover" these mechanisms
    with minimal human intervention and characterize them in detail using the HDP-AR-HMM while 
    \textit{simultaneously} providing a method to estimate diffusion constants.

    %r1_comment3
    %BJC: not sure if I should ignore the JCTC part completely or basically just say what the editor said.
    %MRS: my response below (Basically, saying what the editor said, in case it is send back out).
    \item \textit{Much of the writing seems more suitable for JCTC rather than JPC. I encourage the
    authors to better emphasize and discuss “new physical insight” and “chemical details”, and spend
    less time on methodology. For example pages 5-16 are all on methodology, yet it is not until 
    Figure 8 of the paper (page 26) that the authors give any description of what the LLC system 
    they are studying is actually composed of. Presumably the LLC is made up of self-assembled 
    monomers (in water) shown in Figure 8a). I would encourage the authors to describe their 
    system more concretely much earlier in the paper... there is also no information on system 
    size, box dimensions, etc.}

    Author reply: We thank the reviewer for encouraging us to include
    more physical insight and further details about our molecular
    simulations. We received feedback from the editor along with these
    comments that the scope of JPC has been expanding, and that the
    methodological details are appropriate.
    We have studied the structure of and transport of solutes within this 
    particular LLC system extensively in our previous work.\cite{coscia_chemically_2019}
    We feel strongly that our current work should 
    emphasize the HDP-AR-HMM as a more general tool for understanding complex dynamics in 
    systems beyond our example system. We would prefer not to cut any methodological details, as
    this would hurt the paper's reproducibility, and lengthening the paper by including additional
    physical insight may narrow the audience willing to dive in.

    %BJC: probably could add a picture of the system. Or is it okay to just reference another
    % paper? I would probably use the same pic anyways or something very similar.
    %MRS: never bad to include pictures of the system, so go ahead.

@@

    We do agree that there are certain basic simulation details that we have neglected to 
    mention. Therefore we have made the following edits to section 2.1 of the methods:

    We added the highlight text to the first sentence of the section:
    \begin{quote}
      We studied transport of solutes in the H\textsubscript{II} phase using \hl{our
      previously developed} atomistic molecular model of four pores in a 
      \hl{$9.4\times9.4\times7.6$ nm} monoclinic unit cell with 10\% water by weight, 
      \hl{totaling 62,000 atoms}.    
    \end{quote}

    We have also added the following text describing the model: %BJC: not actually added yet
    \begin{quote}
    %BJC: this is verbatim from last response to reviewers so far
    We modeled water molecules using the TIP3P water model,~\cite{jorgensen_comparison_1983}
    We used the Antechamber module shipped with AmberTools18 to parameterize monomers and 
    solutes using the Generalized Amber Force Field (GAFF).~\cite{wang_development_2004} We 
    assigned charges using the AM1-BCC model
    %MRS: added (here, not in text)
    as implemented in Antechamber.~\cite{jakalian_fast_2000,jakalian_fast_2002}
    GAFF is very commonly used in simulations with diverse organic chemical functionality, 
    and was developed for consistency within the AMBER ecosystem, which uses TIP3P as the
    water model. We chose these standard force fields and generalizable parameterization 
    approaches so that a range of solutes and monomers could be self-consistently and easily 
    studied. 
    %BJC: The following wasn't explicitly asked for, so I could omit
    %MRS: I think it's appropriate to include.
    The main goal of this work is to develop stochastic models which can reproduce
    solute behavior on MD time scales, independent of the choice of force field. In future 
    work, it may be beneficial to employ specialized force fields, including polarizable 
    force fields or other higher-order effects in order to improve the accuracy of structure 
    parameters and selectivity predictions.
    \end{quote}

@@

    %r1_comment4
    \item \textit{The authors should more clearly note that their discussion largely applies only 
    to very low water content LLC regimes (such as the 10\% LLC studied). For higher water content 
    LLCs (e.g. $>$ 15-20\%) it is straightforward to obtain the diffusion limit from standard MD 
    simulations. While the authors are surely well aware of this, the reader may not be, and it is
    important to clearly distinguish the regimes.}

    Author reply: We thank the reviewer for making this point. In higher water content systems, 
    the time scales necessary to reach a diffusive regime will be much more attainable with 
    standard MD.
    %MRS2: is this always the case?  I think a more appropriate response would be "in systems with relatively unimpeded cores, such as in many cases LLCs with a higher water content, most waters will be relatively unimpeded, and diffusion constants can be obtained by standard techniques.   
    However, we do contend that our method would still be very useful for studying
    solute dynamics in these higher water content systems.
    %MRS: maybe "including the dynamics of solutes that have longer residence times and interact with portions of the system away from the pore center."
    Interactions characterized by different
    dynamical behavior even on short time scales can still be highly informative. This is the
    basis for the point we make in the introduction:``...direct calculations of diffusion 
    constants may obscure the molecular mechanisms controlling transport". Therefore we would
    prefer not to limit the range of application of this method. 
    %BJC: If it would be better to modify the text, then we could add something to the effect: If you only care about diffusivity, then this level of
    % modeling isn't necessary in many systems.
    %MRS: I think good to talk about.
    %r1_comment5
    \item \textit{In the HDP-AR-HMM method, it is not clear to me how the solute molecules are 
    constrained to be confined within the pore radius (which they must be on physical grounds 
    based on steric interactions). From Figure 2, it “looks” like this happens to work out, but
    for more complicated systems (e.g. gyroid LLCs with 3D channels) such a constraint may be 
    necessary and it is unclear how the method would generalize. This should be discussed.}

    Author reply: We thank the reviewer for posing this question as this a constraint to which 
    we gave thought but neglected to emphasize in the main text. 
    %BJC: he's not saying that solutes should stay in the aqueous pore region right? We talk pretty
    % extensively about solute behavior in the tails so his steric argument is confusing me.

    %MRS: It is a little confusing. First, we never use the term "pore
    %radius", since the structure of the pore makes it very hard to
    %define a single pore radius.  The term "pore region" is used once
    %(about line 995), that that should probably be "pore center".
    %Second, it's not clear what is meant when they say it's not clear
    %how they are constrained when they must be by steric
    %interactions.  Since steric interactions do NOT keep them in the
    %pore region (at least for the smallest solutes).  Figure 2 is a selection of a trajectory.

    %    First, we would like to clarify
%    that our simulations suggest that small solutes can partition out of the pores and into
%    the dense tail region. This is not a particularly favorable move as evidenced by our radial
%    distribution functions, but it does happen and could conceivably lead to rare jumps of solutes
%    between pores (although we have not observed any).

    %MRS: how about this?  We are grateful for the opportunity to
    clarify some of the details of the simulation geometries.  We
    avoid defining a ``pore radius'' in most cases, since many solutes
    can easily partition partially into the pores, and the radial
    distribution of head groups and even tail groups is changes over
    several angstroms.~\cite{yourpapers} This partitioning occurs to the extent that smaller molecules like water and methanol can in fact
    move between pores in rare instances.~\cite{yourpapers} However the rarity of the events and the fact that they occur parallel to transport means that they do not really affect transport, and can be interpreted mathematically as simply going deep into the wall and coming back again into the same pore.

    Because of this, our stochastic simulations are constrained to remain close to a single pore by the trajectory generation procedure.
    Each state is parameterized by a mean in the radial direction computed based on the solute's 
    distance from the \textit{nearest pore center}, making it impossible for the solute to get 
    further than
    %MRS: maybe this instead?
    %the pore radius.
    half the pore-to-pore distance away.
    %MRS: though I'm not QUITE sure that's right, since the hexagonal packing means that the transition between pores
    %occurs at different distances depending on the angle. 
    Each time a state change occurs, the mean position of the
    solute in the $r$ dimension jumps to the appropriate mean. However, in the axial direction, 
    we do not parameterize the mean since it should be unbounded in that dimension. The $z$ mean
    of each segment is set based on the position immediately before the state change occurred.

    The generalization of this procedure to three dimensions will be under active investigation 
    in the near future. As mentioned, we are interested in applying this approach to bicontinuous
    cubic phases like the gyroid. Based on our current understanding, we would model solute dynamics
    in three dimensions and set the mean vector, $\mathbf{c}$ equal to $\mathbf{0}$. Of course, this
    may result in solutes exploring a three dimensional shape that does not share the geometric 
    features of the studied phase. Our hypothesis is that we can add one or more additional 
    dimensions to the time series passed to the HDP-AR-HMM that includes a distance from the pore centers. 
    We could define the pore center using a spline or a surface and transitions would likely
    favor moves towards states that exist closer to the pore interiors. Alternatively, it may prove
    necessary to constrain solute positions to the means in each dimension. However, these extension
    are beyond the scope of the current paper.
    %MRS: below not really needed.
    %would require 
    %much more data and would likely require us to explore less expensive models as described in
    %the response to Reviewer 2 below.

@@

    \item \textit{There are no units on Figure 1 y-axis, presumably these are nanometer like the 
    other figures?}

    Author reply: We thank the reviewer for catching our oversight. We double-checked the 
    other plots in the paper and found the same mistake on the y-axes of Figure 5. Units of nanometers
    have been added to the y-axes of both plots.

    %r1_comment8
    \item \textit{Figure captions need to be improved. Wording such as “we plotted...”, “we 
    calculated...”, “We also analyzed...” should be omitted in figure captions.}  
    % BJC: This seems like the reviewer forcing his own style on us. And seems like a generalization
    % based on only looking at figure 8. I could just modify parts of figure 8 to please him. But I
    % think the rest are fine. What do you think?

    %MRS: So, I think they have a partial point, in that the caption
    %should describe the figure, and the conclusions proved by the
    %figure, not the process used to get to the figure so much.  So maybe figure 8 should be "hydrogen bonds donated to the methanol to the highlighted oxygen atoms in three regions of the monomer are are shown: the carboxylate . . For each type of hydrogen bond in each predominant state, we show the 95th percentile of hydrogen bond lifetimes."  Does that make sense?

@@

    %r2_comment1
    \item \textit{This paper presents an approach to study transport mechanisms of solutes within
    membranes by applying the sticky hierarchical Dirichlet process autoregressive hidden Markov model
    (HDP-AR-HMM) to molecular dynamics simulation trajectories spanning long times (5 microseconds). 
    Using this method, the authors reveal different dynamic states associated with the transport of 
    solute across a membrane, and interpret them on the basis of solute-membrane interactions. The 
    paper is clear, well written, and relevant to the Journal of Physical Chemistry. I only have a 
    couple of suggestions and minor corrections:}

    Author reply: We thank the reviewer for their kind assessment of our work.

    %r2_comment2
    \item \textit{A motivation for the study is providing a computational tool to guide experimentalists
    in designing membrane materials. However, given the length of the molecular dynamics simulations 
    required, it is presumably impractical to carry a large-scale screening in this way. It would be 
    useful if the authors were more explicit about the role of this approach in guiding experiments, 
    and what would be its advantages and limitations compared to a purely experimental search.}

    Author reply: We thank the reviewer for pushing us to further evaluate the practicality of our
    method as a tool for experimentalists. In short, there are many ways we can envision that 
    would make this approach more amenable to high throughput simulations. The length of our 
    simulations in this paper are indeed quite long. The dynamics of the solutes are somewhat 
    slow and we wanted to ensure we gathered enough data for a sufficient parameterization. 
    Putting aside brute force high throughput simulations that could be enabled by the 
    ever-increasing availability of HPC resources, it would be to our benefit to use the system
    in this work as a benchmark to explore much less expensive models.
    %MRS: maybe focus more on understanding mechanisms, rather than screening?  So the length is not SO impractical.
    We propose some ideas to this end in the text we have added to the end of Section 2.1, where
    our simulations are described:
    \begin{quote}
    In consideration of our ultimate goal, which is to use high-throughput simulations to 
    facilitate our understanding of LLC membrane design for solute-specific separations, the size 
    of our system and length of the accompanying molecular simulations appears to be somewhat 
    impractical.
    We would like to emphasize that our large, fully atomistic models will be
    extremely valuable as a benchmark systems used to explore less expensive models. For example, we 
    could explore systems built with fewer LLC monomers by making the membrane pores shorter. We 
    could also build systems with higher concentrations of solutes in order to gather more 
    dynamical data on shorter timescales. Using what we have learned about the radial distribution
    functions of these solutes in this and our previous work~\cite{coscia_chemically_2019}, it may be possible to 
    learn how to create initial configurations with solutes initially distributed in a way that
    is close to their equilibrium distribution, allowing solutes to thoroughly explore the 
    accessible membrane structural space more quickly and reducing the amount of unequilibrated
    data that must be discarded. % could mention GCMC?
    %MRS: sure.
    Finally, it may be possible to speed up our simulations by 
    reducing the number of atoms using united-atom representations of the liquid crystal monomers.
    %BJC: How strong of an influence would hydrogen mass repartitioning have on hydrogen bonding?
    %, or by using hydrogen mass repartitioning to allow us to increase the MD time step. 
    %MRS: zero on hydrogen bonding strength, which is thermodynamics.  It may affect H-bonding kinetics by
    % increasing the timescales of tumbling (larger rotational inertia, slower rotational diffusion).  If molecules aren't free to tumble anyway, though,
    % then the kinetics may be affected less. 
    \end{quote}

@@

    %r2_comment4    
    \item \textit{As two very minor corrections, in page 15 line 8 it should say "Method 1", and in 
    page 17 line 5 the angle should be H-D-A.}

    % BJC: reviewer is right, VMD docs are misleading: https://www.ks.uiuc.edu/Research/vmd/plugins/hbonds/
    Author reply: We thank the reviewer for pointing out our potential errors. For the hydrogen bond
    criteria we have updated the text from ``D-H-A" to ``H-D-A". Regarding page 15 line 8 (``Method 2:
    Since trajectories generated by Method 2..."), changing ``Method 2" to ``Method 1" would actually be 
    incorrect. At the beginning of Section 2.4, we defined two techniques for generating stochastic 
    trajectories. ``Method 2'' on page 15 line 8 describes the bootstrapping procedures for Method 2 of
    trajectory generation. This is a clear lack of clarity on the author's part and therefore we 
    have made an effort to modify our wording to avoid confusion.

    First, we added additional clarification before describing the bootstrapping procedure (added text
    is highlighted in red):
    \begin{quote}
    Our bootstrapping procedure varied dependent on the method of trajectory generation. \textcolor{red}{
    The following procedures correspond to the methods described above:}
    \end{quote}

### 2020-08-08 Ben_Manuscripts/hdphmm/response_to_reviewers.tex

    We have also modified the text on page 15 line 8 from the original text:
    \begin{quote}
    Since trajectories generated by Method 2 are based on the clustered parameter set used to define a
    single model, we can bootstrap on trajectory ensembles of arbitrary size.
    \end{quote}
    to:
    \begin{quote}
    Since in our second approach to stochastic trajectory generation described above we use clustered 
    parameter sets to define each model, we can bootstrap on trajectory ensembles of arbitrary size.
    \end{quote}

@@

\end{enumerate}

\bibliographystyle{ieeetr}
\bibliography{hdphmm}

\end{document}

% LocalWords:  Subdiffusive Solute Nanoscale Coscia leftmargin FBM vy
% LocalWords:  subdiffusion CTRW sFBM ref solutes antechamber solute
% LocalWords:  polarizable LLC intramolecular quasiharmonic BJC JCTC
% LocalWords:  tex fontsize evy Methanol's selectivities MSDDM arXiv
% LocalWords:  parametrization MSDs MSD timescales renormalizing MFPT
% LocalWords:  bicontinuous Donnan steric em dt lyotropic Calderon al
% LocalWords:  subdiffusive Nanostructured nanoporous TEKMC Phys Chem
% LocalWords:  Venkat Ganesan DBP timescale Webb diffusivities HDP AR
% LocalWords:  HMM nanoparticles penetrants nanoparticle JPC pic LLCs
% LocalWords:  diffusivity gyroid solute's nanometer nanometers HPC
% LocalWords:  carboxylate Dirichlet unequilibrated GCMC VMD docs

### 2020-08-09 Ben_Manuscripts/hdphmm/Draft.tex
Incorporating MRS comments/suggestions

  In this work, we are particularly interested in the design of lyotropic liquid 
  crystal (LLC) monomers, a class of amphiphilic molecules whose ordered self-assembled
  phases can be cross-linked into mechanically strong membranes capable of highly 
  selective separations. Inverted hexagonal phase, or H\textsubscript{II}, LLC membranes
  are characterized by hexagonally packed, uniform-sized and straight pores, an ideal
  geometry for high throughput transport. Their pores are lined with the LLC monomer's
  functional groups which can potentially be designed to interact with solutes in a 
  chemically-specific manner. It would be extremely useful to experimentalists if we 
  could connect LLC monomer design with measurable quantities such as diffusivity and
  selectivity. This goal is complicated by the non-Brownian hopping and trapping behavior
  induced by the membrane's diverse topology and inhomogeneous structure resulting in 
  subdiffusive behavior out to multiple microseconds of simulation.~\cite{coscia_understanding_2019,coscia_chemically_2019}

@@

  %r1_comment3  
  We modeled water molecules using the TIP3P water model,~\cite{jorgensen_comparison_1983}
  We used the Antechamber module shipped with AmberTools18 to parameterize monomers and 
  solutes using the Generalized Amber Force Field (GAFF).~\cite{wang_development_2004} We 
  assigned charges using the AM1-BCC model.~\cite{jakalian_fast_2000,jakalian_fast_2002}
  GAFF is very commonly used in simulations with diverse organic chemical functionality, 
  and was developed for consistency within the AMBER ecosystem, which uses TIP3P as the
  water model. We chose these standard force fields and generalizable parameterization 
  approaches so that a range of solutes and monomers could be self-consistently and easily 
  studied. The main goal of this work is to develop stochastic models which can reproduce
  solute behavior on MD time scales, independent of the choice of force field. In future 
  work, it may be beneficial to employ specialized force fields, including polarizable 
  force fields or other higher-order effects in order to improve the accuracy of structure 
  parameters and selectivity predictions.

@@

  The size and chemical functionality of the solutes dictates the interactions which
  influence solute transport. Figure~\ref{fig:hbonds_assoc_summary} shows that the
  solutes donate hydrogen bonds and associate with sodium ions to varying degrees.
  In fact methanol interacts the least by these mechanisms by far. This is likely 
  because methanol is very small and it is easier for it to partition into the tail
  region where there are fewer groups with which it can interact (see Figure~\ref{fig:rdf_summary}).
  Acetic acid, urea and ethylene glycol are slightly larger than methanol and contain 
  multiple polar substituents which stabilize them closer to the pore region.
  These three solutes also participate in significantly more sodium ion association. 
  In our previous work, we showed that sodium ions frequently associate with the 
  carbonyl groups of acetic acid and urea because the carbonyl oxygen atoms are
  unshielded and have a relatively high partial negative charge.~\cite{coscia_chemically_2019}

>>>>

  In this work, we are particularly interested in the design of lyotropic liquid 
  crystal (LLC) monomers, a class of amphiphilic molecules whose ordered self-assembled
  phases can be cross-linked into mechanically strong membranes capable of highly 
  selective separations. Inverted hexagonal phase, or H\textsubscript{II}, LLC membranes
  are synthesized with 10 \% water by weight and are characterized by hexagonally packed,
  uniform-sized and straight pores, an ideal geometry for high throughput transport. 
  Their pores are lined with the LLC monomer's functional groups which can potentially 
  be designed to interact with solutes in a chemically-specific manner. It would be 
  extremely useful to experimentalists if we could connect LLC monomer design with 
  measurable quantities such as diffusivity and selectivity.
  %r1_comment4
  In many systems, including LLC membranes with higher water contents, making this 
  connection is a relatively straightforward calculation since small solutes and water
  can move relatively unimpeded and therefore enter a diffusive regime on timescales
  accessible to MD. When possible, we encourage the reader to take advantage of the
  simplest approach possible.
  However, in the systems of interested to us,
  this goal is complicated by the non-Brownian hopping and trapping behavior induced by the membrane's diverse
  topology and inhomogeneous structure resulting in subdiffusive behavior out to 
  multiple microseconds of simulation.~\cite{coscia_understanding_2019,coscia_chemically_2019}

@@

  %r1_comment3  
  We modeled water molecules using the TIP3P water model,~\cite{jorgensen_comparison_1983}
  We used the Antechamber module shipped with AmberTools18 to parameterize monomers and 
  solutes using the Generalized Amber Force Field (GAFF).~\cite{wang_development_2004} We 
  assigned charges using the AM1-BCC model as implemented in Antechamber.~\cite{jakalian_fast_2000,jakalian_fast_2002}
  GAFF is very commonly used in simulations with diverse organic chemical functionality, 
  and was developed for consistency within the AMBER ecosystem, which uses TIP3P as the
  water model. We chose these standard force fields and generalizable parameterization 
  approaches so that a range of solutes and monomers could be self-consistently and easily 
  studied. The main goal of this work is to develop stochastic models which can reproduce
  solute behavior on MD time scales, independent of the choice of force field. In future 
  work, it may be beneficial to employ specialized force fields, including polarizable 
  force fields or other higher-order effects in order to improve the accuracy of structure 
  parameters and selectivity predictions.

@@

  The size and chemical functionality of the solutes dictates the interactions which
  influence solute transport. Figure~\ref{fig:hbonds_assoc_summary} shows that the
  solutes donate hydrogen bonds and associate with sodium ions to varying degrees.
  In fact methanol interacts the least by these mechanisms by far. This is likely 
  because methanol is very small and it is easier for it to partition into the tail
  region where there are fewer groups with which it can interact (see Figure~\ref{fig:rdf_summary}).
  Acetic acid, urea and ethylene glycol are slightly larger than methanol and contain 
  multiple polar substituents which stabilize them closer to the pore center.
  These three solutes also participate in significantly more sodium ion association. 
  In our previous work, we showed that sodium ions frequently associate with the 
  carbonyl groups of acetic acid and urea because the carbonyl oxygen atoms are
  unshielded and have a relatively high partial negative charge.~\cite{coscia_chemically_2019}
